Tropical Andes montane and lowland forest bird and mammal species GBIF

### 2023-08-02 code/L0/L0_TropicalAndes_frugivores_GBIF.Rmd
update introduction information update reading in Frugivoria species list and download

---
title: "Tropical Andes montane and lowland forest bird and mammal species GBIF"
author: "Hazel J. Anderson"
collaborators: "None"
data input: "None"
data output: "TropAndes_GBIF_frugivore_occ.csv"
project: "Frugivoria"
date: "2023-04-06"
output: html_document
---

@@

# Read in IUCN data
Data was obtained from https://www.iucnredlist.org/search?permalink=f4407d96-c039-413a-8d46-707f262271ee
```{r}
frugivore_habitats <- read.csv(file.path(data_path,"IUCN/Tropical Andes Birds and Mammals - Search Results/habitats.csv"))
```

# Create species list from IUCN data
```{r}
frugivore_species <- unique(frugivore_habitats$scientificName)
write.csv2(frugivore_species, file = file.path(output_path, "TropicalFrugivoreSpecies.csv"))
```

# Match species names to GBIF
```{r}
gbif_taxon_keys <- frugivore_species %>% 
name_backbone_checklist() %>% # match to backbone 
filter(!matchType == "NONE") %>% # get matched names
pull(usageKey) 
```

@@

# Retrive GBIF download, save file, and load into r
```{r}
d <- occ_download_get("0154158-230224095556074", path = output_path) %>%
  occ_download_import()
```

@@

# Write data to csv
```{r}
TropicalAndes_GBIF_path <- file.path(output_path,"TropAndes_GBIF_frugivore_occ.csv") 
write.csv(d, file = TropicalAndes_GBIF_path)
TropicalAndes_GBIF_species_path <- file.path(output_path,"TropAndes_GBIF_frugivore_occ_species.csv") 
write.csv(GBIF_occ_SpeciesList, file = TropicalAndes_GBIF_path)
```

>>>>

---
title: "Tropical Andes montane and lowland forest bird and mammal species GBIF"
author: "Hazel J. Anderson"
project: "Plant-Frugivore Diversity"
collaborators: "Beth E. Gerstner, Phoebe L. Zarnetske"
overview: "This script retrives plant occurrence data from GBIF using the species list from Frugivoria."
data input: "TropicalAndes_Frugivoria_frugivore_traits_species.csv"
data output: "TropicalAndes_GBIF_frugivore_occ.csv and TropicalAndes_GBIF_frugivore_occ_species.csv"
date: "2023-07-25"
output: html_document
---

@@

# Read in Frugivoria species list
```{r}
frugivore_species <- read.csv(file.path(data_path,"TropicalAndes_Frugivoria_frugivore_traits_species.csv"))
```

# Match species names to GBIF
```{r}
gbif_taxon_keys <- frugivore_species$x %>% 
name_backbone_checklist() %>% # match to backbone 
filter(!matchType == "NONE") %>% # get matched names
pull(usageKey) 
```

@@

# Retrive GBIF download, save file, and load into r
```{r}
d <- occ_download_get("0129743-230530130749713", path = output_path, overwrite = TRUE) %>%
  occ_download_import()
```

@@

# Write data to csv
```{r}
write.csv(d, file = file.path(output_path,"TropicalAndes_GBIF_frugivore_occ.csv"))

write.csv(GBIF_occ_SpeciesList, file = file.path(output_path,"TropicalAndes_GBIF_frugivore_occ_species.csv"))
```
